Software Architectures to Integrate Workflow Engines in Science Gateways

### 2016-04-25 paper.tex
Improved display of notes and closed notes.

\usepackage[x11names,dvipsnames,table]{xcolor} %for use in color links
\usepackage[subrefformat=parens,labelformat=parens]{subfig}
\usepackage{svg}
\usepackage{url}
\usepackage{flushend}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{pbox}

\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\newcommand{\todo}[1]{\color{blue}\xspace[\emph{#1}]\xspace\color{black}}
\newcommand{\note}[2]{\textbf{\Large{\color{blue}\footnote{{\color{blue}\textbf{#1:} \textit{#2}\color{black}}}}}}
\newcommand{\closednote}[4]{}

@@

Architectures showing reduced system complexity will greatly
facilitate the implementation effort towards robust interactions
which, in turn, have a positive impact on characteristics such as
gateway predictability, transparence, general reliability and results
traceability and reproducibility; characteristics that are also key to
a good user experience. \closednote{Marc-Etienne}{I find that
  something is weak in this last paragraph. Robustness will help with
  transparency, sure, but it seems only a small facet.  Also, the text
  seem to timidly favor architectures with less
  components/interactions without much explanation... Complex systems
  can be robust, but at greater costs...  Here is one: "Architectures
  showing reduced system complexity will greatly facilitate the
  implementation effort towards robust interactions which, in turn,
  have a positive impact on characteristics such as gateway
  predictability, transparence, general reliability and results
  traceability and reproducibility; characteristics that are also key
  to a good user experience."}{Tristan}{Agreed.}

>>>>

\usepackage[x11names,dvipsnames,table]{xcolor} %for use in color links
\usepackage[subrefformat=parens,labelformat=parens]{subfig}
\usepackage{svg}
\usepackage{url}
\usepackage{flushend}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{pbox}
\usepackage{pdfcomment}

\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\newcommand{\todo}[1]{\color{blue}\xspace[\emph{#1}]\xspace\color{black}}
\newcommand{\note}[2]{\pdfmargincomment[color=yellow,author=#1,open=true]{#2}}
\newcommand{\closednote}[4]{\pdfmargincomment[color=gray,author=#1-#3,open=true]{#1: #2 \textCR \textCR #3: #4}}

@@

Architectures showing reduced system complexity will greatly
facilitate the implementation effort towards robust interactions
which, in turn, have a positive impact on characteristics such as
gateway predictability, transparence, general reliability and results
traceability and reproducibility; characteristics that are also key to
a good user experience. \closednote{Marc-Etienne}{I find that
  something is weak in this last paragraph. Robustness will help with
  transparency, sure, but it seems only a small facet.  Also, the text
  seem to timidly favor architectures with less
  components/interactions without much explanation... Complex systems
  can be robust, but at greater costs...  Here is one: "Architectures
  showing reduced system complexity will greatly facilitate the
  implementation effort towards robust interactions which, in turn,
  have a positive impact on characteristics such as gateway
  predictability, transparence, general reliability and results
  traceability and reproducibility; characteristics that are also key
  to a good user experience."}{Tristan}{Agreed, fixed as suggested.}
